Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Byzantium revision (\YellowPaperVersionNumber{})}}

### 2018-01-20 Paper.tex
Update explanations of \homesteadmod and \expdiffsymb with citations for EIPs

Note that $\mindifficulty$ is the difficulty of the genesis block. The \textit{\href{https://github.com/ethereum/EIPs/blob/master/EIPS/eip-606.md}{Homestead}} difficulty parameter, $\homesteadmod$, is used to affect a dynamic homeostasis of time between blocks, as the time between blocks varies, as discussed below. $\expdiffsymb$ results in the difficulty increasing every 10000 blocks, which puts upward pressure on the time between blocks, causing it to slowly accelerate, and putting time pressure on transitioning to proof-of-stake. This effect was explained in EIP-649\cite{EIP-649} and implemented earlier in EIP-2\cite{EIP-2}.

>>>>

Note that $\mindifficulty$ is the difficulty of the genesis block. The \textit{Homestead} difficulty parameter, $\homesteadmod$, is used to affect a dynamic homeostasis of time between blocks, as the time between blocks varies, as discussed below, as implemented in EIP-2 \cite{EIP-2}. In the Homestead release, $\expdiffsymb$ results in the difficulty increasing every 10000 blocks, which puts upward pressure on the time between blocks, causing it to slowly accelerate, and putting time pressure on transitioning to proof-of-stake. This effect, known as the "difficulty bomb", or "ice age", was explained in EIP-649 \cite{EIP-649} and delayed and implemented earlier in EIP-2 \cite{EIP-2}. $\homesteadmod$ was also modified in EIP-100 with the use of $x$, the adjustment factor above, and the demoninator 9, in order to target the mean block time including uncle blocks \cite{EIP-100}.
